%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%section settings

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]


%\titleformat{\section}{
%  \vspace{-8pt}\scshape\raggedright\large
%}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\small #2} \\
      \textit{\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & {\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Subhash C. Kantamneni} \\ \vspace{1pt}
    \small \href{mailto:subhashk@mit.edu}{\raisebox{-0.2\height}\faEnvelope\  \underline{subhashk@mit.edu}} ~
    \href{https://subhashk.com/}{\raisebox{-0.2\height}\faBookmark\ \underline{subhashk.com}}  ~
    \href{https://subhashk.com/}{\raisebox{-0.2\height}\faLinkedin\ \underline{sckant}}  ~
    \href{https://github.com/subhashk0}{\raisebox{-0.2\height}\faGithub\ \underline{subhashk01}}
    \vspace{-8pt}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {MIT Sloan School of Management}{2021 -- 2022}
      {MFin, Financial Engineering}{Cambridge, MA}
  \resumeSubHeadingListEnd
  \begin{itemize}
    \itemsep-5pt
    \item \textbf{Activities \& Societies:} Quantitative Financial Markets Club, MFin Capital Builders, India Business Club
    \item \textbf{Courses:} 15.470 Asset Pricing, 15.085 Probability, 15.433 Financial Markets, 15.458 Financial Data Science
  \end{itemize}

\vspace{-16pt}

  \resumeSubHeadingListStart
    \resumeSubheading
	  {Massachusetts Institute of Technology (MIT)}{2018 -- 2021}
	  {SB, Mathematics with Computer Science (Minor: Finance); GPA: 4.8/5.0}{Cambridge, MA}
	\resumeSubHeadingListEnd
	\begin{itemize}[noitemsep]
		\item \textbf{Activities \& Societies:} MIT Pokerbots, MIT Consulting Group, Phi Kappa Theta Fraternity
		\item \textbf{Courses:} 15.457 Advanced Analytics of Finance, 15.438 Fixed Income Securities \& Derivatives, 6.046 Algorithms, 18.100Q Real Analysis, 18.650 Statistics, 18.404 Theory of Computation, 18.703 Algebra
	\end{itemize}

\vspace{-16pt}

  \resumeSubHeadingListStart
    \resumeSubheading
      {Princeton University}{2017 -- 2018}
      {Dual Enrollment, Mathematics; GPA: 3.7/4.0; Courses: Honors Linear Algebra, Number Theory}{Princeton, NJ}
  \resumeSubHeadingListEnd
  
%\vspace{-16pt}

%-----------WORK EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {DRW}{Jun -- Aug 2021}
      {Quantitative Trading Analyst Intern}{Greenwich, CT}
      \resumeItemListStart
        \resumeItem{\textbf{Project:} Researched signals and trading strategies for US Treasury Options/Futures on the Global Macro Vol desk.}
        \resumeItem{\textbf{Skills:} Interest rate derivatives, macro trading, backtesting, statistical analysis, technical analysis.}
      \resumeItemListEnd

    \resumeSubheading
      {Morgan Stanley}{Jun -- Aug 2020}
      {Institutional Equity Summer Analyst}{New York, NY}
      \resumeItemListStart
        \resumeItem{\textbf{Projects:} Implemented ETF trading strategy and binary classifier for dynamic option Gamma hedging in Python.}
        \resumeItem{\textbf{Shadowing:} Index Derivatives, Single Name Options, ETFs, and Automated Market Making trading desks.}
        \resumeItem{\textbf{Skills:} Derivatives pricing, option Greeks, option strategies, and quantitative risk management.}
    \resumeItemListEnd
    
    \resumeSubheading
      {Seven Eight Capital}{May -- Aug 2019}
      {Quantitative Developer Intern}{New York, NY}
      \resumeItemListStart
        \resumeItem{\textbf{Project:} Built, studied, and evaluated multi-factor asset pricing models for US and European equities.}
        \resumeItem{\textbf{Skills:} Python (Pandas), data science (regression analysis, model selection, outliers), and BARRA risk models.}
      \resumeItemListEnd
    
  \resumeSubHeadingListEnd

% \vspace{-16pt}

%-----------PROGRAMMING SKILLS-----------
 \section{Skills \& Interests}
  \begin{itemize}[leftmargin=0.0in, label={}]
     \small{\item{
      \textbf{Typescript} \hspace{0.3in} {Well-trained in creating clean, maintainable code and industry style automated unit testing} {\vspace{0.015in}}\\
      \textbf{Python} {\hspace{0.588in}}{Utilized extensively for research projects, specifically the Matplotlib, SciPy, and NumPy libraries} \vspace{0.015in}\\
      \textbf{C} {\hspace{0.945in}} {Created Arduino projects including a self-driving vehicle and a web integrated light-sound alarm clock} \vspace{0.015in}\\
      \textbf{Other} {\hspace{0.7025in}}{Linux, Command line Git, Bash Scripting, and submitting batch jobs} \\
     }}
  \end{itemize}


% \vspace{-16pt}

%-----------EXTRACURRICULAR EXPERIENCE---------------
\section{Extracurricular Experience}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {MIT Pokerbots}{Sep 2018 -- Present}
      {President (2019 - 2021), Sponsorship Director (2018 - 2019)}{Cambridge, MA}
      \resumeItemListStart
        \resumeItem{Led team of seven members to successfully run four-week computer poker class and competition for 250 MIT and Harvard undergrad/grad students. Managed operations and developed 2021 game engine.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

% \vspace{-16pt}

%-----------AWARDS-----------
\section{Awards}
\begin{itemize}[leftmargin=0.15in, label={}]
	\small{\item{
			\textbf{MIT MFin Fellowship} {Awarded in recognition of outstanding academic record, achievements and professional promise.} \\
			\textbf{Young Naturalist Awards} {Individually top 6 nationwide for high school biology research.} \\
			\textbf{Olympiads} {2 time AIME qualifier, USACO Gold Division.} \\
			\textbf{Tournament of Champions} {Two time qualifier in Public Forum Debate (national high school championships).}
	}}
\end{itemize}


  
%  \vspace{-16pt}

\end{document}